Code to reproduce results in _Semi-parametric generalized linear model for

### 2021-08-16 ManuscriptCode/Manuscript.Rmd
Cleaner output for manuscript

```{r setup, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE, autodep=TRUE)

library(exchreg, quietly=TRUE)
library(knitr, quietly=TRUE)
library(dplyr, quietly=TRUE)
library(tidyr, quietly=TRUE)
library(ggplot2, quietly=TRUE)
theme_set(theme_classic())

library(CorrBin, quietly=TRUE) ## utilities for working with correlated binomial data
library(VGAM, quietly=TRUE) ## for beta-binomial regression
library(geepack, quietly=TRUE)  ## for GEE

set.seed(20210814)
```

@@

```{r Table1}
table1 <- data.frame(GEE = cbind(Est = coef(ba_gee), SE=sqrt(diag(vcov(ba_gee)))),
                BB = cbind(Est = coef(ba_bb)[-2],      # second value is logit(rho)   
                           SE=sqrt(diag(vcov(ba_bb)))[-2]),  
                SPGLM = cbind(Est = coef(ba_spglm), SE=ba_spglm$SE))
kable(table1, digits=3)
```

@@

  nms <- names(coef(res_spglm))
  res <- bind_rows(
    GEE = tibble(Term = nms, 
                 Est=coef(res_gee), 
                 SE = sqrt(diag(vcov(res_gee)))),
    BB = tibble(Term = nms,
                Est = coef(res_bb)[-2],      # second value is logit(rho)   
                SE=sqrt(diag(vcov(res_bb)))[-2]),
    SPGLM = tibble(Term = nms,
                   Est = coef(res_spglm), 
                   SE=res_spglm$SE),
    .id = "Model")
  res
}
```

@@

```{r ActualSim}
R <- 2

@@

```{r ComparePlot}
ggplot(comb, aes(x=Model, y=Est, colour=Model)) +
  facet_grid(Generator~Term) +
  geom_hline(aes(yintercept=Correct)) +
  geom_jitter(alpha=0.3, height=0)
```

>>>>

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE, autodep=TRUE)

library(exchreg)
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_classic())

library(CorrBin) ## utilities for working with correlated binomial data
library(VGAM) ## for beta-binomial regression
library(geepack)  ## for GEE

set.seed(20210814)
data(boric_acid)
```

@@

```{r Table1a}
table1 <- list(GEE = cbind(Est = coef(ba_gee), SE=sqrt(diag(vcov(ba_gee)))),
                BB = cbind(Est = coef(ba_bb)[-2],      # second value is logit(rho)   
                           SE=sqrt(diag(vcov(ba_bb)))[-2]),  
                SPGLM = cbind(Est = coef(ba_spglm), SE=sqrt(diag(vcov(ba_spglm)))))
table1
```

```{r Table1, eval=FALSE}
table1 <- data.frame(GEE = cbind(Est = coef(ba_gee), SE=sqrt(diag(vcov(ba_gee)))),
                BB = cbind(Est = coef(ba_bb)[-2],      # second value is logit(rho)   
                           SE=sqrt(diag(vcov(ba_bb)))[-2]),  
                SPGLM = cbind(Est = coef(ba_spglm), SE=sqrt(diag(vcov(ba_spglm)))))
kable(table1, digits=3)
```

@@

  nms <- names(coef(res_spglm))
  res <- bind_rows(
    GEE = tibble(Term = nms, 
                 Est=coef(res_gee), 
                 SE = sqrt(diag(vcov(res_gee)))),
    BB = tibble(Term = nms,
                Est = coef(res_bb)[-2],      # second value is logit(rho)   
                SE=sqrt(diag(vcov(res_bb)))[-2]),
    SPGLM = tibble(Term = nms,
                   Est = coef(res_spglm), 
                   SE= sqrt(diag(vcov(res_spglm)))),
    .id = "Model")
  res
}
```

@@

```{r ActualSim}
R <- 50

@@

```{r ComparePlot}
ggplot(comb, aes(x=Model, y=Est, colour=Model)) +
  facet_grid(Generator~Term) +
  geom_hline(aes(yintercept=Correct)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha=0.3, height=0)
```

# Session information
```{r Info}
sessionInfo()
```
